% Copyright 2015 Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Themes: moderncv
\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}

%% Character Encoding
% replace by the encoding you are using
\usepackage[utf8]{inputenc}

%% Page Layout
\usepackage[scale=0.8]{geometry}

%% Personal Data
\firstname{Byung-Jin}
\familyname{Park}
\address{(omitted for web)}{(omitted for web)}
\mobile{(+82) 10-9030-1843} 
\email{posquit0.bj@gmail.com}
\homepage{http://posquit0.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CONTENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%% TITLE
\maketitle

%% EDUCATION
\section{EDUCATION}
\cventry{}{POSTECH(Pohang University of Science and Technology)}{Pohang, S.Korea}{}{}{}

%% PROFESSIONAL EXPERIENCES
\section{PROFESSIONAL EXPERIENCES}
\cventry{Aug. 2014 -- PRESENT}{R.O.K Cyber Command, MND}{Seoul, S.Korea}{}{}{}
\cventry{Jan. 2013 -- Feb. 2013}{NEXON}{Seoul, S.Korea \& LA, U.S.A}{}{}{}
\cventry{Dec. 2011 -- Feb. 2012}{ShiftOne Corp. (Start-up company)}{Seoul, S.Korea}{}{}{}
\cventry{Jul. 2012 -- Jun. 2013}{Software Maestro (held by Korean government)}{Seoul, S.Korea}{}{}{}
\cventry{Nov. 2011 -- PRESENT}{B10S (B1t 0n the Security, Underground hacker team)}{S.Korea}{}{}{}
\cventry{Jul. 2012 -- PRESENT}{WiseGuys (Hacking \& Security research group)}{S.Korea}{}{}{}
\cventry{}{UNUS}{S.Korea}{}{}{}
\cventry{}{SAMSUNG Electronics}{S.Korea}{}{}{}
\cventry{}{}{S.Korea}{}{}{}

%% WRITING & PRESENTATION
\section{WRITING \& PRESENTATION}{}{}{}{}
\cventry{Jan. 2015 -- PRESENT}{A Guide for Developers in Start-up}{Facebook Page}{}{}{}
\cventry{Oct. 2012 -- Jul. 2013}{AhnLab}{S.Korea}{}{}{}
\cventry{Jul. 2012}{CodeEngn (Reverse Engineering Conference)}{Seoul, S.Korea}{}{}{}

%% EXTRACURRICULAR ACTIVITIES
\section{EXTRACURRICULAR ACTIVITIES}{}{}{}{}
\cventry{Jun. 2010 -- PRESENT}{PoApper(Developers' Network of POSTECH)}{Pohang, S.Korea}{}{}{}
\cventry{Sep. 2013 -- PRESENT}{MSSA(Management Strategy Club of POSTECH)}{Pohang, S.Korea}{}{}{}
\cventry{Sep. 2010 -- Oct. 2011}{PLUS(Laboratory for UNIX Security in POSTECH)}{Pohang, S.Korea}{}{}{}

%% HONORS & AWARDS
\section{HONORS \& AWARDS}
\cventry{}{DEFCON CTF Hacking Competition World Final}{Las Vegas, U.S.A}{}{}{}
\cventry{Jul. 2012}{SECUINSIDE Hacking Competition World Final}{Seoul, S.Korea}{}{}{}
\cventry{Nov. 2013}{KISA HDCON Hacking Competition Final}{Seoul, S.Korea}{}{}{}

%% ACTIVITY
\section{ACTIVITY}
\cventry{}{}{}{}{}{}

%% LINKS
\section{Links}
Github:// \\
LinkedIn:// \\

%% SKILLS
\section{Skills}
\cvline{Language}{Native Korean, Fluent in English (TOEIC: 750), Beginner in Japanese}
\cvline{Programming}{}
\cvline{Certificates}{}
\cvline{Others}{}

\end{document}
