%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Alert Logic} % Organization
    {Cardiff – London, United Kingdom} % Location
    {Nov. 2016 – PRESENT} % Date(s)
    {
      Design, implement and test efficient and scalable software to be run in a distributed environment. Drive challenging development processes within a multinational team, taking ownership over technical activities inside the team. Help manage task distribution within a small team and drive the implementation effort to complete business goals and deliver high-quality results. Interview engineer position candidates. Mentor junior software engineers. Major areas of responsibility include:
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {AWS Marketplace Metering and Contract services integration.}
        \item {Sales and finance integration (Zuora, SalesForce).}
        \item {Service side HTTP core libraries.}
        \item {Backend AWS integration.}
        \item {Provisioning development and continuous integration infrastructure.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Alert Logic} % Organization
    {Cardiff, United Kingdom} % Location
    {Aug. 2013 – Nov. 2016} % Date(s)
    {
      Designed, implemented and tested fast and scalable software that run in a distributed environment. Was responsible for deployed software components in the field, being on on-call rotation for emergency escalations. Participated in challenging development process within cross geographical teams. Contributed to multiple projects including:
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {AWS Marketplace SaaS integration.}
        \item {Billing and metering services.}
        \item {Generalized Data Sources and Asset Map service.}
        \item {Data collection, configuration and collection alert services.}
        \item {Windows agent eventlog collector.}
        \item {User alert notification service.}
        \item {HTTP reverse proxy service.}
        \item {API throttling service and its integration.}
        \item {Customer API authentication.}
        \item {Assets provisioning API.}
        \item {3rd party clients integration (Zuora, SalesForce and etc).}
        \item {Continuous integration automation.}
        \item {Core libraries and web service components for handling, authentication and data processing.}
        \item {Cloud/On-premises deployment automation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Reksoft} % Organization
    {St. Petersburg, Russia} % Location
    {Aug. 2013 – Feb. 2015} % Date(s)
    {
      Designed, implemented and tested fast and scalable software that run in a distributed environment. Was responsible for deployed software components in the field, being on on-call rotation for emergency escalations. Participated in challenging development process within cross geographical teams. Contributed to multiple projects including:
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Microsoft Azure marketplace resource provider.}
        \item {Account management and provisioning API, including integration with 3rd party services, such as SalesForce, Siteminder, LDAP and etc.}
        \item {Customer usage and entitlements audit tools and services.}
        \item {Distributed assets provisioning API.}
        \item {Customer-facing assets management integration APIs, including interactive documentation portal.}
        \item {Common web service utilities and core components for handling, authentication and data processing.}
        \item {Deployment automation using chef cookbooks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Sperasoft} % Organization
    {St. Petersburg, Russia} % Location
    {Apr. 2013 – Jul. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop, troubleshoot and maintain NHL14 logic and screens.}
        \item {Support multiple platforms (PS, XBOX).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Devline Limited} % Organization
    {Krasnodar, Russia} % Location
    {Jul. 2008 - Apr. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Refactored and maintained a library for video archive export through VFW using C++}
        \item {Designed and implemented a library for video archive export through ffmpeg using C++}
        \item {Refactored, maintained and optimized DirectShow source filter}
        \item {Created software for packaging and reading protected resource container using WinCrypt}
        \item {Implemented autorun program using C++ and HTMLayout}
        \item {Created serial number activation application using C++, WinHTTP}
        \item {Designed, implemented and optimized user log module (client + server sides) using C++ and SQLite}
        \item {Implemented SQLite tokenizer using C}
        \item {Created skins support including implementation of a specific one in collaboration with designers}
        \item {Developed, optimized and maintained the main CCTV client side application using C++ and HTMLayout}
        \item {Developed localization system for the HTML based application using Python, C++ and HTMLayout}
        \item {Designed and implemented automatic build system using Python}
        \item {Designed and maintained internal automation utilities using Python}
        \item {Wrote developers and integration documentation}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
