%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Frontend developer} % Job title
    {Nil foundation} % Organization
    {Yerevan, Armenia (remote)} % Location
    {May. 2022 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \vspace{8pt}
      \item[] {\small\textit{Nil Foundation is an Ethereum L2 startup working on Ethereum horizontal scalability.}}
      \vspace{8pt}
        \item {Built from scratch and released proof market DEX-like interface (React, Redux, Redux-saga), which is a decentralized exchange of computation powers for proofs generation.}
        \item {Built a block explorer for the NIL Layer 2 chain with detailed views for blocks, transactions, and accounts. Designed and optimized the frontend architecture for performance and scalability. Also contributed to the Node.js backend powering the explorer.}
        \item {Developed an interactive, sharding-specific smart contract playground for the NIL chain. The tool enables users to write and compile Solidity code, save snippets, deploy contracts, and interact with them — all within a unified interface.}
        \item {Built a custom JavaScript SDK for interacting with the Nil blockchain, tailored to support SSZ serialization and Poseidon hashing. This library became the foundation for multiple critical tools, including a CLI, Hardhat plugin, and browser wallet extension.}
        \item {Developed and maintained the corporate website using Next.js with a Strapi CMS backend, along with additional marketing pages to support product outreach.}
        \item {Created and maintained a reusable React UI component library, adopted across nearly all NIL interfaces to ensure design consistency and development efficiency.}
        \item {Participated a lot in building and maintaining CI/CD pipelines using Github actions CI, Ansible and Jinja}
      \end{cvitems}
    }
    {\vspace{16pt}}

%---------------------------------------------------------
  \cventry
    {Frontend developer} % Job title
    {InfoTeCS JSC} % Organization
    {Saint Petersburg, Russia} % Location
    {Jun. 2021 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \vspace{8pt}
      \item[] {\small\textit{InfoTeCS is a cybersecurity company providing a range of secure communication solutions for corporate clients.}}
      \vspace{8pt}
        \item {Built Remote Work Management System, a big internal React app, where employees could request remote work, track approval pipelines, and submit daily reports. I created interfaces, pages and forms, worked on performance optimizations and managed API workflows with Redux Saga. I also contributed to backend C\# controllers and validations to support frontend logic. }
        \item {Contributed to Employee performance evaluation system - a large-scale web application built with ASP.NET and a legacy frontend stack using jQuery and Backbone.js.}
        \item {Led frontend development for a Next.js documentation portal targeting foreign branches, combining static site generation with dynamic internal routing. This portal was a key touchpoint between the company and its foreign customers. One part of the app was public-facing, the other integrated into an internal doc system.}
        \item {Maintained React components library and closely collaborated with Design department to ensure consistent implementation of the design system.}
      \end{cvitems}
    }
    {\vspace{16pt}}

%---------------------------------------------------------
  \cventry
    {Frontend engineer intern} % Job title
    {InfoTeCS JSC} % Organization
    {Saint Petersburg, Russia} % Location
    {Mar. 2021 - Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed React-based Artifact Management App. This internal tool allowed teams to upload, download, and manage build artifacts across multiple systems. All existing artifacts were aggregated in a dynamic responsive table with server-side sorting and filtering, making it easy for engineers to quickly locate, and interact with the files.}
      \end{cvitems}
    }
    {\vspace{16pt}}

%---------------------------------------------------------
  \cventry
    {Frontend developer} % Job title
    {Freelance} % Organization
    {Saint Petersburg, Russia} % Location
    {Sept. 2020 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed a Vue2 and Vuetify-based monitoring service, integrating interactive Leaflet maps for real-time data visualization and location tracking.}
        \item {Developed and maintained multiple static and PHP-based marketing and business websites as an independent contractor, collaborating directly with clients.}
      \end{cvitems}
    }
    {\vspace{16pt}}

%---------------------------------------------------------
\end{cventries}
