% !TeX root = ../cv.tex

\cvsection{Conferences \& schools}

\begin{cventries}

	\cventry
	{SUMMER SCHOOL}
	{8th Mathematica Summer School on Theoretical Physics - Random Matrix Theory and applications}
	{Berlin, Germany} % Location
	{Aug. 15th 2016 - Aug. 19th 2016} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item {Held at Hulbolt University, a week before IGST2016}
			\item {Main lecturers included Nikolay Gromov (King's College London), Vladimir Kazakov (ENS Paris), Alexander Migdal (Migdal LLC) and others.}
		\end{cvitems}	
	}
	
	\cventry
	{SUMMER SCHOOL}
	{2015 European School on Magnetism - From basic magnetic concepts to spin currents}
	{Cluj-Napoca, Romania} % Location
	{Aug. 24th 2015 - Sep. 4th 2015} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item {Organizing committee included CEA-Grenoble center, NEEL Institute, Babes-Bolyai University and Technical University of Cluj-Napoca}
			\item {Main lecturers include Michael Coey (Trinity College Dublin), Steve Blundell (University of Oxford) and others.}
		\end{cvitems}	
	}
	
	\cventry
	{FIELD INTERSHIP}
	{II Estágio de Campo na Serra da Estrela} % Title
	{Serra da Estrela, Portugal} % Location
	{Aug. 24th 2015 - Sep. 4th 2015} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item {Awarded students were given the opportunity of talking and living for 3 days with scientists that worked on polar regions}
			\item {Workshops on different topics like Arctic/Antarctic biology and geologic formation of \emph{Serra da Estrela}}
			\item {Coordinated by Gonçalo Vieira (Universidade de Lisboa) and with the participation of marine biologist José C. Xavier (Universidade de Coimbra), Vanessa Batista (Ciência Viva) and Alexandre Trindade (Universidade de Lisboa)}
		\end{cvitems}	
	}
		
	
\end{cventries}