%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
  {Finance Data Engineer} % Job title 
  {DHL Group} % Organization
  {Bonn, Germany} % Location 
  {Jan. 2021 - Present} % Date(s) 
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      % \item {Key role in technology adoption for tech-trends as machine learning, generative \& applied AI.}
      \item {Implemented a finance-specific RAG chatbot using LangChain and ChatGPT, providing access to guidelines, timelines and process documentation for finance teams.}
      \item {Served as the primary maintainer for an advanced data analytics tool, supporting production forecasting processes and enabling data-driven decision-making.}
      \item {Completed multiple time series forecasting projects, optimizing key financial KPIs by using machine learning and statistical models.}
      \item {Designed and developed data pipeline workflows, improving efficiency, data quality, and processing speed for finance operations.} 
      \item {Built a custom Python-based TM1 API wrapper to automate the retrieval of time series data from IBM TM1 reporting servers.} 
      \item {Transformed an automated finance report filing and creation system impacting approx 300 users when transitioned from iShare to Sharepoint Online with Office365.}
      \item {Facilitated internal knowledge-sharing workshops, educating teams on best practices in Python development and machine learning implementation, driving upskilling across the organization.} 
    \end{cvitems} 
  }

  
%---------------------------------------------------------
\cventry
  {Junior Finance Expert} % Job title
  {DHL Group} % Organization
  {Bonn, Germany} % Location
  {May 2018 - Dec. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Central role in Finance IT, acting as an middleman between the controllers and finance systems.}
      \item {Build multiple modern financial reports with variable inputs from a IBM TM1 Server inferface.}
      \item {Administered the finance data warehouse server in self-service.}
      \item {Responsible for multiple process optimization projects using modern workflow tools.}
      % \item {Created countless business presentations for higher management with emphasis on data analysis and strategic steering.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
{Research Assistant} % Job title
{Centre for Finance, Risk- \& Resource Management} % Organization
{TU Dortmund University, Germany} % Location
{Oct. 2015 - Sep. 2017} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    % \item {Implemented an webscraper to build a Option Chain database in R.}
    % \item {Build an volatility estimator for intraday data in Python.}
    % \item {Designed a \LaTeX~template for BA and MA theses compliant for the chairs requirements.}
    \item {Contributed to the chairs publications and assisted in scientific research.
    % Contributions include:
    %   \begin{itemize}
    %     \item[$\cdot$] Shiny survey app for \textit{"Retirement strategies under life expectation shocks"} 
    %     \item[$\cdot$] Visualizations using gg2plot in R for \textit{"A Game Theory Application on Package Asset Auctions"}
    %   \end{itemize}
    }
    % \item {Co-Corrector for the chairs written exams.}
    \item {Caretaker of the chairs intern SQL databases.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
