\cvsection{Extracurricular Activity}
\begin{cventries}
  \cventry
    {Core Member}
    {B10S (B1t 0n the Security, Underground hacker team)}
    {S.Korea}
    {Nov. 2011 - PRESENT}
    {
      \begin{cvitems}
        \item {Gained expertise in penetration testing areas, especially targeted on web application and software.}
        \item {Participated on a lot of hacking competition and won a good award.}
        \item {Held several hacking competitions non-profit, just for fun.}
      \end{cvitems}
    }
  \cventry
    {Member}
    {WiseGuys (Hacking \& Security research group)}
    {S.Korea}
    {Jun. 2012 - PRESENT}
    {
      \begin{cvitems}
        \item {Gained expertise in hardware hacking areas from penetration testing on several devices including wireless router, smartphone, CCTV and set-top box.}
        \item {Trained wannabe hacker about hacking technique from basic to advanced and ethics for white hackers by hosting annual Hacking Camp.}
      \end{cvitems}
    }
  \cventry
    {Core Member \& President at 2013}
    {PoApper (Developers' Network of POSTECH)}
    {Pohang, S.Korea}
    {Jun. 2010 - PRESENT}
    {
      \begin{cvitems}
        \item {Reformed the society focusing on software engineering and building network on and off campus.}
        \item {Proposed various marketing and network activities to raise awareness.}
      \end{cvitems}
    }
  \cventry
    {Member}
    {PLUS (Laboratory for UNIX Security in POSTECH)}
    {Pohang, S.Korea}
    {Sep. 2010 - Oct. 2011}
    {
      \begin{cvitems}
        \item {Gained expertise in hacking \& security areas, especially about internal of operating system based on UNIX and several exploit techniques.}
        \item {Participated on several hacking competition and won a good award.}
        \item {Conducted periodic security checks on overall IT system as a member of POSTECH CERT.}
        \item {Conducted penetration testing commissioned by national agency and corporation.}
      \end{cvitems}
    }
  \cventry
    {Member}
    {MSSA (Management Strategy Club of POSTECH)}
    {Pohang, S.Korea}
    {Sep. 2013 - PRESENT}
    {
      \begin{cvitems}
        \item {Gained knowledge about several business field like Management, Strategy, Financial and marketing from group study.}
        \item {Gained expertise in business strategy areas and inisght for various industry from weekly industry analysis session.}
      \end{cvitems}
    }
\end{cventries}
