%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Thesis}

%-------------------------------------------------------------------------------
% SUBSECTION TITLE
%-------------------------------------------------------------------------------
% \cvsubsection{B. Sc. Thesis}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {A Handful of Factors: The Construction of the Fama-French Five-Factor-Model for the German Stock Market} % Affiliation/role
    {M. Sc. Thesis}
    {} % Location
    {Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {The thesis conducts a comprehensive asset pricing study based on Compustat data for the German stock market obtained from Wharton Research Data Services. The research investigates whether a Fama French five-factor model can explain average returns in the German stock market. Furthermore, the study tests the performance of a five-factor model against that of the CAPM, Fama French three-factor model and the Carhart four-factor model. It is shown, that all models perform well on explaining the average returns on portfolios sorted by size and book-to-market ratio.  The study provides more evidence that return factors are indeed country specific.} % For the period 1992 to June 2017 it is shown that }
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Testing the Efficient Market Hypothesis for Soccer Odds in Germany} % Affiliation/role
    {B. Sc. Thesis}
    % {Deutscher Handballbund (DHB)} % Organization/group
    {} % Location
    {Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {The thesis proposed the question if the European market for soccer betting odds was efficient. The research takes a look at the six biggest, most important soccer leagues in Europe and analyzed over 2000 betting odds in the season 2013/14. It is shown, when more bookmakers entered the market the profit margin vanished over the years. The work concludes that arbitrage is almost non-existent and that there are not profitable betting strategies since the market is ex-post efficient.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
