%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
\begin{itemize}
 \item {Expertise of Agile Testing \textbf{Selenium} and \textbf{Web Services} Automation Tool with 6+ years exp.}

 \item {Selenium used with \textbf{PHP, Java, C\#.net, TypeScript} and developed frame work for each.}

 \item {Created Framework \textbf{SeUnit,NuanceDriver} Using Selenium Web driver and Java.}

 \item {\textbf{Migration} of existing framework from RC to Webdriver.}

 \item {Using \textbf{Gauge} framework and tweaking to work with \textbf{CLIFramework} using jSch as per the need of the framework.}

 \item {Hands-on of \textbf{Sahi \& VSTS} Automation Tool and \textbf{Linux/Shell} scripting.}

 \item {Worked on corporate banking, email marketing and analytics application.}

 \item {OWASP Testing using ZAP tools}

 \item {Highly organized, versatile and results-oriented team player with an energetic and articulate approach to testing. \textbf{Quick learner}, good communication skills, interpersonal skills, leadership skills.}

 \item {Have strong problem solving capabilities and analytical skills.}

 \item {Handled Team of 5 persons with their tasks and planning.}
 
 \item {Leading as QA to a new project at Nuance, automation done with Protractor and Cucumber in TypeScript.}
\end{itemize}
\end{cvparagraph}
a