%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Volunteeering}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Founder \& Organizational Lead} % Affiliation/role
    {DeSci Boston Conference} % Organization/group
    {2021 - Present} % Location
    {Boston, Massachusetts U.S.A} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Successfully raised all necessary funding for the first year of the conference, ensuring the event took place by securing sponsorships, organizing venues, coordinating speakers, and managing attendee logistics.}
        \item {Established and managed a series of committees for the second year of the conference, overseeing a team of 10 and managing the finances to drive strategic initiatives and ensure operational excellence.}
        \item {Managed a global community of 500+ members, fostering a cohesive and engaged network of participants and stakeholders.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Founder \& Organizational Lead} % Affiliation/role
    {DeSci Amsterdam Conference} % Organization/group
    {2021 - 2022} % Location
    {Amsterdam, Netherlands} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Successfully raised all necessary funding for the conference, securing sponsorships and partnerships with leading industry organizations.}
        \item {Expertly organized all event logistics, including venue selection, speaker coordination, and attendee management, ensuring a seamless experience.}
        \item {Efficiently managed day-of operations for a 300+ person event, overseeing a team of volunteers and staff to deliver a high-quality, engaging conference.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sotheby's Liaison} % Affiliation/role
    {ConstitutionDAO} % Organization/group
    {2020} % Location
    {New York City, New York U.S.A} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Helped spin up a team of 30 people who crowdsourced \$50M in 7 days from 30,000 individual contributors to buy a copy of the U.S. Constitution at auction.}
        \item {Served as the liaison between the core team and Sotheby's, the auction house responsible for the copy of the Constitution.}
        \item {Managed a community of 30,000 people across various social platforms, fostering engagement and communication.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
