%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Freelance consultant Devops & Automation Engineer} % Job title
    {For BNP PARIBAS CIB division} % Organization
    {Paris, France} % Location
    {Dec. 2023 - Dec. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with team members to ensure effective performance monitoring and observability across the organization.}
        \item {Implemented and maintained Dynatrace solutions for comprehensive application and infrastructure monitoring.}
        \item {Utilized Git for version control, maintaining configuration files and scripts related to Dynatrace configurations.}
        \item {Leveraged Ansible for automation, streamlining the deployment and management of Dynatrace across various environments.}
        \item {Played a key role in optimizing system performance and identifying areas for improvement through Dynatrace insights.}
        \item {Worked collaboratively to enhance overall observability strategies, ensuring a proactive approach to issue detection and resolution.}
        \item {Contributed to the development and implementation of best practices for utilizing Dynatrace tools within the team.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Freelance consultant Devops} % Job title
    {Canal Plus. (Groupe Bolloré)} % Organization
    {Paris, France} % Location
    {Aug. 2023 - Dec. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a DevOps Engineer, led the implementation of end-to-end CI/CD pipelines using tools such as Ansible, Jenkins, Git, and Jira.}
        \item {Utilized Git for version control, implementing and maintaining CI/CD workflows for efficient solution code deployment.}
        \item {Introduced and championed best practices in CI/CD, evangelizing the importance of automation and continuous integration throughout the development lifecycle.}
        \item {Played a key role in migrating version control systems, leading the transition from Bitbucket to GitLab. Conducted successful proof of concept for migrating CI/CD processes from Jenkins to GitLab CI.}
        \item {Introduced SonarQube for code quality analysis, enhancing the overall development process.}
        \item {Collaborated with cross-functional teams, leveraging Jira for efficient project management and issue tracking.}
        \item {Continuously optimized and streamlined deployment processes, ensuring faster and more reliable delivery of software solutions.}
        \item {Contributed to the development and implementation of best practices for DevOps processes within the team and organization.}
        \item {Worked closely with diverse departments to ensure the smooth transition to a hybrid cloud model, addressing unique business requirements and fostering collaboration between teams.}
        \end{cvitems}
        
    }

%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer} % Job title
    {Adyoulike Inc.} % Organization
    {Paris, France} % Location
    {Feb. 2023 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a Site Reliability Engineer, managed a multicloud environment spanning OVH, AWS, GCP, and on-premises infrastructure.}
        \item {Maintained and optimized the performance and reliability of critical technologies, including Apache Mesos, Kafka, Docker, and Hadoop for big data processing.}
        \item {Successfully implemented ScyllaDB over MongoDB on Ubuntu 18.04, enhancing database efficiency and scalability.}
        \item {Led the migration of Apache Airflow to Google Kubernetes Engine (GKE) on Google Cloud Platform (GCP), ensuring a seamless transition and improved orchestration capabilities.}
        \item {Collaborated with cross-functional teams to maintain and support legacy systems, ensuring high availability and reliability in a complex, multicloud architecture.}
        \item {Played a pivotal role in crafting and executing a migration strategy, addressing challenges specific to a multicloud environment and diverse technology stack.}
        \item {Contributed to the development of SRE best practices, emphasizing reliability, scalability, and efficient incident response.}
      \end{cvitems}
      
    }

%---------------------------------------------------------
  \cventry
    {Integration Engineer \& Big Data administrator } % Job title
    {Société Générale} % Organization
    {Paris, France} % Location
    {Mar. 2020 - Sept. 2022 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As an Integration Engineer in a Hadoop production environment, played a crucial role in designing, deploying, and optimizing complex data processing systems.}
        \item {Utilized Ansible and Git to automate and accelerate the delivery process, particularly in a high-critical business domain focused on banking fraud detection.}
        \item {Maintain Kafka as the Event driver for real-time data streaming, enabling efficient communication and data flow within the Hadoop ecosystem.}
        \item {Maintain HBase as a NoSQL Database, providing scalable and distributed storage for large volumes of data generated in the context of banking fraud analytics.}
        \item {Led the first migration from legacy deployment practices to a modern Continuous Integration/Continuous Deployment (CI/CD) approach.}
        \item {Championed the integration of CI/CD practices to streamline and enhance the software development lifecycle.}
        \item {Faced challenges during the CI/CD adoption process, including overcoming legacy system dependencies, ensuring backward compatibility, and aligning with stringent security and compliance requirements in the banking fraud detection domain.}
        \item {Collaborated with cross-functional teams to address difficulties, establish best practices, and ensure a smooth transition to modern CI/CD builds.}
        \item {Contributed to the development of robust CI/CD pipelines, incorporating automated testing, deployment strategies, and version control to ensure the reliability and efficiency of software releases.}
      \end{cvitems}
      
    }

%---------------------------------------------------------
\cventry
{Infrastructure Engineer} % Job title
{BNP Paribas and BP2I Division} % Organization
{Paris, France} % Location
{Jan. 2018 - Mar. 2019} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implemented Splunk solutions on-premise for BNP Paribas and its BP2I division.}
    \item {Led the Git implementation to control code in a CI perspective.}
    \item {Deployed and tested in CI/CD using GitLab CI pipelines.}
    \item {Deployed infrastructure using Ansible, ensuring efficient and consistent deployment processes.}
    \item {Collaborated with cross-functional teams to design and deploy scalable and secure infrastructure.}
    \item {Utilized version control systems, specifically Git, to manage configuration files and infrastructure code.}
    \item {Worked on optimizing system performance, identifying and resolving infrastructure-related issues.}
    \item {Contributed to the development and implementation of best practices for infrastructure management.}
    \item {Collaborated with team members to enhance overall system observability and monitoring.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{System Administrator} % Job title
{Synalabs} % Organization
{City, Country} % Location
{Start Date - End Date} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Managed and administered web hosting systems for various clients at Synalabs.}
    \item {Configured, maintained, and monitored web servers, including Apache and Nginx.}
    \item {Installed and managed databases, including MySQL and PostgreSQL, to ensure optimal performance of hosted websites.}
    \item {Implemented robust security measures, including firewall configuration, SSL certificate management, and proactive vulnerability monitoring.}
    \item {Automated recurring tasks using custom scripts and automation tools.}
    \item {Provided technical support to clients for resolving hosting-related issues, including connectivity, performance, and security problem resolution.}
    \item {Collaborated with development teams to ensure effective deployment and management of web applications.}
    \item {Implemented reliable backup strategies and data recovery in case of disasters.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{DevOps Engineer} % Job title
{Freelance Consultant - Devops Engineer}
{Deveryware} % Organization
{Paris, France} % Location
{June 16 - Aug 17} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implementation of a dual authentication system to enhance the security of an application.}
    \item {Proactive maintenance of the geolocation solution to ensure availability and reliability.}
    \item {Utilization of a fully open-source environment: Proxmox, GitLab CE, Jenkins.}
    \item {Deployment and management of infrastructure using HashiCorp tools to ensure scalability and security.}
    \item {Close collaboration with the team to establish DevOps best practices in project workflows.}
    \item {Integration and optimization of HashiCorp tools to enhance deployment and management processes.}
    \item {Contributions to the continuous improvement of team practices and overall project efficiency.}
  \end{cvitems}
}


%---------------------------------------------------------
\cventry
{Freelance Consultant - System Engineer - } % Job title
{AB Tasty} % Organization
{Paris, France} % Location
{Dec 15 - June 16} % Dates
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Managed and maintained MySQL databases in a multi-cloud environment.}
    \item {Focused primarily on services hosted on AWS, using Elastic Beanstalk for deployment.}
    \item {Worked extensively with the Aurora Database for data storage and retrieval.}
    \item {Introduced Docker into infrastructure practices to enhance scalability and efficiency.}
    \item {Led the process of migrating from MySQL to MariaDB for improved database solutions.}
    \item {Collaborated with cross-functional teams to ensure seamless integration of services on AWS.}
    \item {Contributed to the adoption of Docker for containerization within the infrastructure.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Exploitation Engineer} % Job title
{Meetic} % Organization
{Paris, France} % Location
{Mars 15- Dec 15} % Dates
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Managed on-premise infrastructure for Meetic, ensuring optimal performance and continuous reliability.}
    \item {Maintained and supported Meetic's solution infrastructure with continuous monitoring and proactive issue resolution.}
    \item {Actively participated within the team in delivering multi-environment solutions, adapting the infrastructure to diverse operational needs.}
    \item {Collaborated closely with cross-functional teams to address and meet infrastructure requirements.}
    \item {Utilized best practices to ensure the scalability and security of the infrastructure supporting Meetic's services.}
    \item {Contributed to the ongoing improvement of infrastructure processes and operational efficiency.}
  \end{cvitems}
}

%------------------------------------------------------------

\cventry
{Ingénieur d'Exploitation} % Titre du poste
{Meetic} % Organisation
{Paris, France} % Lieu
{March 15 - Dec. 15} % Dates
{
  \begin{cvitems} % Description(s) des tâches/responsabilités
    \item {Gestion de l'infrastructure sur site pour Meetic, assurant des performances optimales et une fiabilité continue.}
    \item {Maintenance et support de l'infrastructure de la solution Meetic, avec une surveillance continue et une résolution proactive des problèmes.}
    \item {Participation active au sein de l'équipe pour la fourniture de solutions multi-environnements, adaptant l'infrastructure aux divers besoins opérationnels.}
    \item {Collaboration étroite avec des équipes interfonctionnelles pour répondre et satisfaire aux exigences de l'infrastructure.}
    \item {Utilisation des meilleures pratiques pour assurer la scalabilité et la sécurité de l'infrastructure supportant les services de Meetic.}
    \item {Contributions à l'amélioration continue des processus d'infrastructure et de l'efficacité opérationnelle.}
  \end{cvitems}
}

%-----------------------------------------------------------------
\end{cventries}
