%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  % ZAPIER
  %---------------------------------------------------------
  \cventry
    {Senior Frontend Engineer} % Job title
    {Zapier, Inc.} % Organization
    {Remote} % Location
    {Nov. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Collaborated across multiple diverse, international teams to develop and release core functionality to improve
          the end-user experience.
        }
        \item {
          Championed a re-write of the legacy core product code to meet new frontend development standards, converting
          the product to a completely Server-Side Rendered application. This re-write provided a platform to develop
          new highly-requested features and eliminated a large amount of existing technical debt.
        }
        \item {
          Collaborated within my team, as well as with the wider engineering department, to extract the core product
          frontend code from a monorepo and convert the code to TypeScript. As part of this, I also built a
          fully-customised CI/CD pipeline, using GitLab and Docker, that automated publishing of NPM packages and
          reduced production deploy times from over an hour to less than 10 minutes.
        }
        \item {
          Worked extensively with technologies such as Typescript, React, Redux, NextJS, GraphQL and Storybook to
          deliver a performant and accessible user experience.
        }
      \end{cvitems}
    }

  %---------------------------------------------------------
  % GENIE SOLUTIONS
  %---------------------------------------------------------
  \cventry
    {Engineering Team Lead} % Job title
    {Genie Solutions Pty Ltd} % Organization
    {Brisbane, Australia} % Location
    {Jul. 2017 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Led a cross-functional product team to design and develop new features for a cloud-based SaaS application.
        }
        \item {
          Implemented Agile principles within the team to increase output velocity by 120\%.
        }
        \item {
          Standardised development languages and practices within the organisation as part of an internal Technical
          Working Group to increase developer efficiency.
        }
        \item {
          Spearheaded integrations with multiple third parties to allow the secure delivery of correspondence between
          doctors while maintaining patient privacy.
        }
        \item {
          Responsible for managing team members' personal and professional development by ensuring they received the
          necessary training and support to perform and improve in their roles.
        }
      \end{cvitems}
    }

  \cventry
    {Full-Stack Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Nov. 2010 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Helped build, from inception to release, a cloud-based SaaS application for the practice management of
          medical professionals.
        }
        \item {
          Developed and deployed microservices across multiple environments to increase the scalability and stability
          of the SaaS product.
        }
        \item {
          Developed an integration with the Australian Department of Human Services to process electronic medical
          claims, allowing doctors to be paid for their services in days rather than weeks.
        }
      \end{cvitems}
    }

  \cventry
    {Customer Support Officer} % Job title
    {} % Organization
    {} % Location
    {Feb. 2008 - Nov. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Interacted with customers as the first point of contact for technical and functional support. Utilised
          excellent problem-solving skills to diagnose and resolve customer issues.
        }
        \item {
          Liaised with various third parties, such as the Australian Department of Human Services and private health
          insurance companies, to help resolve customer issues.
        }
      \end{cvitems}
    }

\end{cventries}
