
Software architect with a critical eye and open mind. I led successful projects in various domains (data management, social networks, mobile apps \& games, robotics \& AI) and teams sizes (2-5 persons), from B2C settings to publicly projects with several million in funds. I shine on the intersection of engineering and product/people/cross-functional leadership \see{n42r.github.io}



\section{Projects}



\cventry{2023 -- 2024}{Muze AI}{Open Source Software}{Independent Project}{}{
\begin{itemize}
\item Conceived and built the first AI/LLM music recommendation tool that does not use Spotify's metadata \see{github.com/n42r/muze-ai}
\end{itemize}}




\vspace{1ex}


\cventry{2022 -- 2023}{Guestrrday}{Open Source Software}{Independent Project}{}{
\begin{itemize}
\item Developed an open source music tagging tool that successfully processed over 20,000 items \see{github.com/n42r/guestrrday}
\end{itemize}}




\vspace{1ex}

\cventry{2019 -- 2023}{The Basin Network}{Architectural Model/Invention}{Doctoral Project}{}{
\begin{itemize}
\item Invented a novel architectural pattern for data cataloging that is more transparent and detailed than state-of-the-art approaches such as data mesh and data lake.
\item Balanced the architecture for data exchange, interoperability, integration, collaboration, standards development, and managing data as an asset.
\item Defended the project and was awarded a PhD with grade of \emph{cum laude} (with praise).
\item Published 2 papers in international conferences.
\end{itemize}}




\vspace{1ex}



\cventry{2015 -- 2019}{SIMUTOOL}{SaaS (B2B)}{EU-Funded Manufacturing Project}{}{
\begin{itemize}
\item Led a team of four to develop a data lake SaaS for a 8-company EU project which enabled close data-driven cooperation and coupling between participating companies \see{github.com/simutool}.
\item Communicated \& collaborated with domain experts to identify requirements.
%\item Enabled streamlined data sharing \& exchange in a consortium of 8 companies.
\item Designed a scalable architecture as well as interfaces, APIs, and data formats.
\item Developed software and led developers using agile methods to build smoothly integrated components.
%\item Communication Onterface between the engineering team and management as well as end users.
\end{itemize}}


\vspace{1ex}

\cventry{2012 -- 2014}{Tawla}{Game/Mobile (B2C)}{Startup (Employment)}{}{%Backgammon board game App on the iOS mobile platform
\begin{itemize}
\item Attained improved App ratings (from 3 to 4.5/5 stars) by building a new Artificial Intelligence (AI) player for the board game \see{n42r.github.io/tw}.
\item Conceived and implemented a complex random number generator for the dice algorithm leading the game to receive good reviews due to less predictable game flow.
%\item \textbf{Roles:} R\&D engineer: developed complex components (ex., AI players, randomization).
%\item \textbf{Results:} The rating of the App improved from 3 to 4+ stars citing the AI players.
\end{itemize}}



\vspace{1ex}

\cventry{2012 -- 2014}{Greetings Studio}{Social Network/Mobile (B2C)}{Startup (Employment)}{}{%Social network/iOS App for creating and sharing e-cards 
\begin{itemize}
\item Supervised the development of a social network which enabled users to create E-Cards and images and share them with others \see{n42r.github.io/gs}.
\item Trimmed turn-over time between user feedback and technical/product iterations by organizing a 10 minute weekly stand-up between marketing and technical teams.
\item Scaled and improved the architecture of the SaaS for maintainability and performance.
%\item \textbf{Roles:} Team leader, technic<al product manager, software architect.
%\item \textbf{Results:} Number of active users \& rating steadily grew to 4 stars on the Apple Store.
\end{itemize}}




%\vspace{1ex}

%\cventry{2010 -- 2011}{ArtSapiens}{R\&D Project (AI/Robotics)}{International RoboCup Competition}{}{Software to compete in the international RoboCup AI Soccer competition.
%\begin{itemize}
%\item R\&D head (architecture, AI, markov models, etc), co-founder, co-leader.
%\item Developed the architecture of the software soccer players.
%\item Designed architecture and led the R\&D of complex components (ex., Markov Models).
%\item \textbf{Roles:} Co-founder of a team of 10+, head of R\&D.
%\item \textbf{Results:} The software qualified and competed in the 2011 RoboCup finals.
%\end{itemize}}


%\vspace{1ex}

%\cventry{2009 -- 2010}{Cassie}{R\&D Project (AI/Robotics)}{Masters Project}{}{Artificial Intelligence reasoning \& control software for robot perception (Stack: LISP)
%\begin{itemize}
%\item \textbf{Results:} Discovered two novel methods, published 2 papers in top conferences.
%\item \textbf{Roles:} Researcher, developer (LISP).
%\end{itemize}}


%\vspace{1ex}
%\cventry{2007}{Knowledge Learner}{Graduation Project}{}{}{A tool to integrate case-based reasoning in machine learning (Stack: C++, Visual Studio).
%\begin{itemize}
%\item Researched and developed the solution .
%\item \textbf{Results:} Improvement on breast cancer and heart attack benchmarks, published paper.
%\end{itemize}}


%\vspace{1ex}
%\cventry{2006}{Walk The Line}{Competition (German University in Cairo)}{}{}{An Obstacle avoidance, maze-navigating vehicle (Stack: Micro-C PIC programming).
%\begin{itemize} 
%\item Developed the control software.
%\item \textbf{Results:} Selected for display in the annual open science day of the university.
%\end{itemize}}



%\vspace{1ex}
%\cventry{2005}{Reversi3D}{Competition (German University in 	Cairo)}{}{}{3D board game of Othello (Stack: Java v5 \& Java3D).
%\begin{itemize}
%\item Developed the whole project, including AI players 
%\item \textbf{Results:} One of the top three in a competition involving 100+ submitted games.
%\end{itemize}}



\section{Employment}

%\cventry{2021 -- 2023}{Freelance | Doctoral Student}{}{}{}{
%\begin{itemize}
%\item Completed a PhD: A data cataloging architectural pattern \see{n42r.github.io/phd}
%\item Developed several independent open source software projects.
%\end{itemize}}

\vspace{1ex}
\cventry{2015 -- 2020}{Research Associate (Architect | Team Lead)}{University of Bamberg}{}{Germany}{
\begin{itemize}
%\item Played a key role in developing a data management solution for a multi-partner project.
\item Led a team to develop a data lake SaaS for a 3.5 million Euro EU manufacturing project, which led to improved data discovery, collaboration, and turn-over time \see{github.com/simutool}.
\item Strengthened relationships with the 10+ end-users (highly qualified professionals with PhDs) which led to better understanding of the domain and their requirements.
\item Designed systems for ease of scalability, integration, and maintainability.
\item Organized the project, planned iterations and milestones, and supervised developers with agile practices to drive continuous growth.
%\item Stack: Neo4j, RDF, Python, Flask, Web2py, Docker (multi-container), git, UML.
%\item Interfaced with and extracted requirements from domain experts.
%\item Served as the single source of truth on the project.
\end{itemize}}

%\vspace{1ex}
%\cventry{2013 -- 2015}{Assistant Dean / Lecturer}{University of Technology Twintech}{}{Yemen}{
%\begin{itemize}
%\item Managed the IT and Multimedia faculties, reporting to the university president.
%\item Led curriculum development initiative for the Business IT and Multimedia faculties.
%\item Courses: \emph{Software Analysis}, \emph{Human-Computer Interaction}, \emph{Information Design}, etc.
%\end{itemize}}


\vspace{1ex}
\cventry{2011 -- 2014}{Team Leader | Software Architect | R\&D Engineer}{TayaIT}{Cairo}{Egypt}{
\begin{itemize}
\item Led agile technical teams ranging in size from 2-4 on two long-term social media / mobile products resulting in continuously increasing app rankings and user base.
\item Strengthened cross-functional collaboration between technical, business, and UI/UX leading to 30\% shorter cycle times, closer cooperation, and increased productivity.
\item Researched and incorporated various state-of-the-art technologies.
%\item Researched and incorporated various state-of-the-art technologies into our stack such as Protege/semantic web
%\item Managed multiple products (social media apps and games) and reported to the CEO.
%\item Designed/maintained the software architectures for the products (UML).
%, with ratings rising from 3 to 4 stars and most positive reviews citing the AI player and the UX/UI.
\end{itemize}}


%\vspace{1ex}
%\cventry{2008 -- 2012}{Teaching Assistant}{The German University in Cairo (GUC)}{Cairo}{Egypt}{
%\begin{itemize}
%\item Taught 10 hours per week of tutorials, interfacing with 150 new students per semester.
%\item Courses: \emph{Introduction to Artificial Intelligence}, \emph{Introduction to Computer Science}, \emph{Introduction to Computer Programming}. 
%\end{itemize}}

\section{Skills}
%\begin{cvcolumns}

%  \cvcolumn{General}{Data Architecture, Product Management, Team Leadership, UML}
%  \cvcolumn{Programming}{Python, Graph Databases, Prolog, lisp}
%\end{cvcolumns}


\cvitem{Hard Skills}{System design, coaching, technical product management, agile/lean, prototyping, research, R\&D, meta-data / data management, domain modeling, knowledge management, change management, data integration, data cataloging.}
\cvitem{Databases}{MongoDB (NoSQL), Neo4j (Graph DB), SQL, Google Firebase Cloud, RDF}
\cvitem{Development}{Python, Docker (multi-container), Linux CLI, git, UML}
\cvitem{Soft Skills}{Critical thinking, empathy, cross-functional collaboration, teamwork, leadership, (technical) communication, problem solving, public speaking, intercultural fluency}
\cvitem{Past Skills}{Lisp, C++, Java, PIC microcontroller programming (embedded)}



\section{Education}
	


\cventry{2023}{PhD. (Dr. rer. nat.)}{Information Systems \& Applied Computer Science, Otto-Friedrich-Universit\"{a}t Bamberg}{Bamberg, Germany}{}{}{}
%\cventry{2023}{PhD (Dr. rer. nat.)}{IS \& Applied Computer Science, Uni. Bamberg}{Germany}{}{}{}  % arguments 3 to 6 can be left empty
%\cvitem{}{\emph{Thesis}: The Basin Network: A next generation data management approach akin to data mesh, data space, and data lake. A data architecture pattern for the interoperable cataloging, governance, and exchange of data. \see{n42r.github.io/phd}}
%\cvitem{}{A data architectural pattern for data cataloging and exchange \see{n42r.github.io/phd}}


\vspace{1ex}
\cventry{2010}{MSc.}{Computer Science \& Engineering, The German University in Cairo}{Egypt}{}{}
%\cvitem{}{Thesis: A framework for robot perception, including computational and algorithmic models. Ex., if a robot hears a baby but does not see it, is there a baby?}


\vspace{1ex}
\cventry{2008}{BSc.}{Computer Science \& Engineering, The German University in Cairo}{Egypt}{}{}



% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): 
%\renewcommand{\refname}{Publications}
%\nocite{*}
%\bibliographystyle{unsrt}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file


\section{Publications}

\cvitem{}{Full list: \urll{scholar.google.com/citations?user=JgS4-1cAAAAJ}}{}

%\cvitem{2021}{Data-Sharing Markets for Integrating IoT Data Processing Functionalities. \emph{CCF Transactions on Pervasive Computing and Interaction}.}{}


%\cvitem{2018}{Semantic Data Management for Experimental Manufacturing Technologies. \emph{Datenbank-Spektrum}.}{}

%\cvitem{2010}{Focused Belief Revision as a Model of Fallible Relevance-Sensitive Perception. \emph{K\"{u}nstliche Intelligenz 2010: Advances in Artificial Intelligence}.}{}

%\cvitem{2010}{High-Level Perception as Focused Belief Revision. \emph{European Conference on AI (ECAI)}.}{}

%\cvitem{}{Published papers in top conferences (European Conference on Artificial Intelligence, CCF Transactions on Pervasive Computing and Interaction, K\"{u}nstliche Intelligenz) in the topics of: data architecture, the IoT, knowledge graphs, and artificial intelligence.}


\section{Languages}

\cvitem{Arabic}{Mother Tongue}
\cvitem{English}{Fluent}
\cvitem{German}{Good understanding, Basic Speaking (B1, Telc Certificate)}


%\section{References}
%\cvitemwithcomment{}{Furnished upon request.}{}

%\cvitemwithcomment{}{\textbf{Daniela Nicklas}, \textit{Chair}, Mobile Software Systems Group, University of Bamberg}{}
%\cvitemwithcomment{}{\textbf{Haythem Ismail}, \textit{Dean}, MET Faculty, The German University in Cairo}{}
%\cvitemwithcomment{}{\textbf{Ashraf Tawwakol}, \textit{Co-founder}, Intersection; formerly, \emph{CEO}, TayaIT}{}
%\cvitemwithcomment{}{\textbf{Wael Alaghbari}, \textit{President}, International University of Technology Twintech}{}



