%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
\definecolor{awesome}{HTML}{008a00}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Jonas}{Falck}
\position{Bioinfornatician - Data Analyst}
\address{Muzenplaats 4, 6525JA, Nijmegen, Netherlands}

\mobile{(+31) 655707314}
\email{jonas@falcken.de}
%\homepage{www.posquit0.com}
\github{joe-nas}
%\linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``rtfm"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {dr. Peter Schaap, Associate professor}
  {Wageningen University \& Research – Department of Agrotechnology and Food Sciences - Systems and Synthetic Biology}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application: Computational Technician Research at Wageningen University \& Research}
% How the letter is opened
\letteropening{Dear dr. Peter Schaap}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Jonas Falck~~~·~~~Motivation}
  {}

% Print the title with above letter informations
\makelettertitle
%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
After completing my civil service duty, I moved from Germany to the Netherlands to study medical biology in Nijmegen. 
I completed my bachelor’s degree and began my master's in medical biology at the Radboud University. 
During this time, both in- and outside of university, I focused on developing IT skills such as setting up and managing headless Linux systems, programming with a focus on bioinformatics, machine learning and dynamic websites. 
I honed my bioinformatic skills during my master's internships in the Radboud UMC human genetics department, as well as in the comparative genomics group. 
Due to financial and personal reasons, I started working in logistics and was unable to finish my master’s degree. 
However, I am determined to pursue my passion for biology and IT and work in a field that allows me to utilize my potential while having a greater societal impact.
Apart from my professional goals, I enjoy concerts, bouldering, brewing kombucha and most importantly, spending time with my friends and family.
\lettersection{Why Computational Research Technician at WUR?}
As a computational research technician at WUR I could combine two fields I am passionate about and work at the intersection of biology and technology.
WUR is a world class University, a hub where cutting-edge research takes place and where generated knowledge is translated into biotechnological, medical and environmental applications.
As a trained biologist with background in human biology who is keen on technology and applied machine learning, I would gladly join your team and your mission.
In your department, I could tackle the technical/coding aspects while also providing support to colleagues.
This vacancy promotes a clean code policy while following FAIR principles. 
Adherence to such principles resonates with me as I believe it is pivotal for efficient, robust and reproducible research.
I value collaborating with international and interdisciplinary teams to exchange knowledge and provide support to each other’s.
I am confident that this is possible at WUR and more so in an inclusive and diverse working environment.
Therefore, I would like to join your team at the Systems and Synthetic Biology department at WUR.
\lettersection{Why Me?}
While my career path may not have been straightforward, I have gained a lot of experience along the way, making me the ideal candidate for this position. 
I am highly motivated to work as a computational research technician, possess experience in data-analysis and application development.
Moreover, I have the knowledge to work on and setup server infrastructure or containerized applications using a variety of programming languages, tools and operating systems.
During my academic journey, I developed a passion for omics data, its analysis, machine learning and the associated technical and computational aspects. 
To handle these aspects effectively, I devoted a significant amount of time to mastering programming/scripting in R, Python, Bash, and the command line
More recently I have expanded my skill set to include JavaScript for API/backend development.
Developing my own R package to streamline data analysis during one of my internships, along with working on hobby projects, online courses and providing support to friends and peers on technical challenges, has provided me with ample experience in troubleshooting complex issues. 
Furthermore, I have experience in communicating bioinformatic methods and results to researchers, regardless of their background in bioinformatics.
I am intrinsically motivated to learn and eager to apply and share the skills showcased in the CV. 
While I value being able to work independently, I also appreciate having knowledgeable peers around to discuss stubborn problems. 
As a hands-on and down-to-earth person, as well as a hard worker, I would be pleased to meet with you soon.

\end{cvletter}
%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing
\end{document}
