%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Cloud \& Automation Consultant} % Job title
    {D2SI} % Organization
    {Paris, France} % Location
    {Oct. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided devops and Docker training as well as support}
        \item {Deployed many infrastructures on Amazon Web Services (EC2, DynamoDB, ECS, ECR, Lambda ...)}
        \item {Designed Docker solutions for development, continuous integration and production environment}
        \item {Automated infrastructures using mainly Terraform, Packer and Bash. But also Ansible and Python}
        \item {Realized continuous integration/deployment platforms with Jenkins (pipeline mode), ContinuousPHP and Drone.io}
        \item {Managed an intern working on Docker related themes such as Data persistency and orchestration solutions benchmarking}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cloud Engineer (Trainee)} % Job title
    {Linagora} % Organization
    {Puteaux, France} % Location
    {Oct. 2015 - Exp. Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built multiple docker-compose's and images for different in-house projects}
        \item {Deployed a Ceph cluster (made of 3 nodes) and integrated it to OpenStack's Cinder storage service}
        \item {Automated a Kubernetes infrastructure on OVH's public cloud platform, based on Terraform and CoreOS}
        \item {Installed a DevStack instance as a quick'n'dirty testing platform}
        \item {Provided Docker 101 formations and support to the other teams}
        \item {Created a private Docker registry using Port.us}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer Engineer (Trainee)} % Job title
    {Thales Services} % Organization
    {Velizy, France} % Location
    {Sept. 2014 - Exp. Sept. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Research and development on the RBAC pattern and introducing it to the team}
          \item {Built a Restful API based on Symfony 2 and a web client using AngularJS 1.4}
          \item {Continuous integration and deployment with Jenkins, SonarQube and Capistrano}
          \item {Researched on the DevOps methodologies and started promoting it to the team}
          \item {Deployed a reverse-proxy for our software factory using HAProxy}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
