\begin{cvletter}
  \cvletterinfo
    {Company Name}
    {Awesome Street 1}
    {Cool Town}
    {Germany}
    {Fancy job title}
    
Dear Mr./Ms./Dr. LastName:

Opening paragraph: State why you are writing; how you learned of the organization or position, and basic information about yourself.

2nd paragraph: Tell why you are interested in the employer or type of work the employer does (Simply stating that you are interested does not tell why, and can sound like a form letter). Demonstrate that you know enough about the employer or position to relate your background to the employer or position. Mention specific qualifications which make you a good fit for the employer’s needs. (Focus on what you can do for the employer, not what the employer can do for you.) This is an opportunity to explain in more detail relevant items in your resume. Refer to the fact that your resume is enclosed. Mention other enclosures if such are required to apply for a position.

3rd paragraph: Indicate that you would like the opportunity to interview for a position or to talk with the employer to learn more about their opportunities or hiring plans. State what you will do to follow up, such as telephone the employer within two weeks. If you will be in the employer’s location and could offer to schedule a visit, indicate when. State that you would be glad to provide the employer with any additional information needed. Thank the employer for her/his consideration.

Sincerely,\newline

Lars Richter
\end{cvletter}
