\cvsection{Education}

\begin{cventries}
\cventry
{Graduation from Primary School} % Degree
{Kildevæld Efterskole} % Institution
{Kolding, Denmark} % Location
{2008 - 2011} % Date(s)
{} % Description(s) bullet points

\cventry
{Graduation from STX} % Degree
{Sønderborg Statsskole} % Institution
{Sønderborg, Denmark} % Location
{2011 - 2014} % Date(s)
{} % Description(s) bullet points

\cventry
{Learning and Experience Technology (no degree)} % Degree
{University of Southern Denmark, SDU} % Institution
{Odense, Denmark} % Location
{2016 - 2018} % Date(s)
{
  \begin{cvitems} % Description(s) bullet points
    \item {Knowledge gained: }
    \begin{itemize} % Description(s) bullet points
      \item {UX and Interaction Design.}
      \item {VR and AR development.}
      \item {Game development with Unity.}
      \item {Web development with JavaScript.}
    \end{itemize}
    \item {Projects: }
    \begin{itemize} % Description(s) bullet points
      \item {\textbf{1st semester:} An Asymmetrical Multiplayer Game developed with GameMaker. It turned out well, and we were asked to showcase it for new students, which was cool.}
      \item {\textbf{2nd semester:} A booking system made as a Node.js web application for a housing cooperative firm that needed a modern way to book out their guest apartment. It was made as a calendar utilizing Bootstrap, different frameworks, and a NoSQL database to save bookings. It is, as far as I know, still used today.}
      \item {\textbf{3rd semester:} A Node.js web app for a simulated primary school project week about bees.}
      \item {\textbf{4th semester:} A toy for children in a kindergarten we worked with. It was a pillow that made sounds when touched. It was made to enhance different kinds of play. It was not very successful, but it was a fun project to work on.}
    \end{itemize}
  \end{cvitems}
}

\cventry
{B.S. in Software Engineering} % Degree
{University of Southern Denmark, SDU} % Institution
{Odense, Denmark} % Location
{2018 - 2021} % Date(s)
{
  \begin{cvitems} % Description(s) bullet points
    \item {Knowledge gained: }
    \begin{itemize} % Description(s) bullet points
      \item {Algorithms and data structures.}
      \item {Architectural and infrastructural patterns.}
      \item {Containerization and clustering.}
      \item {Operating systems and network.}
      \item {Programming paradigms and languages.}
      \item {Software engineering principles, practices, tools, and techniques.}
    \end{itemize}
    \item {Projects: }
    \begin{itemize} % Description(s) bullet points
      \item {\textbf{1st Semester:} A clone of the game Bubble-Struggle written in Java with object-oriented patterns and the 3-layer architecture.}
      \item {\textbf{3rd semester:} A web app for students wanting to study abroad. A map with universities worldwide, where a user could click on a university to get cultural information and the big-mac index compared to their origin country.}
      \item {\textbf{4th semester:} A boss fighter game utilizing the OSGi framework to make every component in the game modular. We made it possible to disable and enable components others depended on by iteratively disabling/enabling dependencies.}
      \item {\textbf{5th semester:} Experts in Teams project concerned with the effect on CO2 emission in a future where migrating fossil-fueled planes to hydrogen-powered planes is possible. }
      \item {\textbf{Bachelor thesis:} I built a generic framework capable of translating one text source into another, e.g., from Java to C\#. The framework was used to generate AnyLogic models for a web-based application (EcosystemMapGenerator) I built for SDU.}
    \end{itemize}
  \end{cvitems}
}

\cventry
{MSc in Software Engineering} % Degree
{University of Southern Denmark, SDU} % Institution
{Odense, Denmark} % Location
{2021 - 2023} % Date(s)
{
  \begin{cvitems} % Description(s) bullet points
    \item {Knowledge gained: }
    \begin{itemize} % Description(s) bullet points
      \item {Big Data Systems}
      \item {Cloud computing}
      \item {DevOps}
      \item {Domain Specific Languages}
      \item {Embedded Systems}
      \item {iOS Development}
    \end{itemize}
    \item {Projects: }
    \begin{itemize} % Description(s) bullet points
      \item {\textbf{7th semester:} A big data system that scraped satellite imagery of beach geo-locations from the Sentinel-2 satellite and processed them to determine how shorelines have changed over time. An Android app was also built to visualize the data.}
      \item {\textbf{8th semester:} A simulated assembly line consisting of a self-constructed crane, a rotating disk, and a web camera. It was programmed by the group's own DSL, which generated a client that could execute the program. The client utilized MQTT to communicate with the embedded system.}
      \item {\textbf{9th semester:} We developed Power Price Assistant, a web app that simulates a system that can advise on what electricity provider to choose based on the user's electricity consumption patterns.}
      \item {\textbf{Master thesis:} A study of whether a data space can be implemented as a data mesh and what benefits and drawbacks it can have for the energy sector in Denmark. A prototype of a data product, the central component of a data mesh, was developed to test the hypothesis. }
    \end{itemize}
  \end{cvitems}
}
\end{cventries}
