%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Stanford University, Online} % Affiliation/role
  {\textit{Machine Learning}}
  {Grade: 87\%} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      %\item {Not understanding a thing during my brother's phd defense about support vector machines inspired me to take this course.}
      \item {11 week course covering go to methods applied in supervised and unsupervised learning, regularization and how to tackle problems like bias and overfitting.}
      \item {Certificate of accomplishment: http://tinyurl.com/v5ytdzhs}
    \end{cvitems}
  }
  \newline
%---------------------------------------------------------
\cventry
  {Kaggle.com, Online Machine-Learning Community} % Affiliation/role
  {\textit{Intro to Machine Learning}}
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      %\item {Not understanding a thing during my brother's phd defense about support vector machines inspired me to take this course.}
      \item {This course covered the basics of machine learning using python giving an introduction in topics such as data exploration, building models, model validation, under and overfitting and random forests.}
      \item {Certificate of accomplishment: https://tinyurl.com/3t9xuxdy}
    \end{cvitems}
  }
  \newline

%---------------------------------------------------------
  \cventry
  {Kaggle.com, Online Machine-Learning Community} % Affiliation/role
  {\textit{Pandas}}
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      %\item {Not understanding a thing during my brother's phd defense about support vector machines inspired me to take this course.}
      \item {This course is dedicated to the pandas python data analysis library and covered useful data manipulation skills.}
      \item {Certificate of accomplishment: https://tinyurl.com/4ec7n95c}
    \end{cvitems}
  }
  \newline

%---------------------------------------------------------
\cventry
{Kaggle.com, Online Machine-Learning Community} % Affiliation/role
{\textit{Data Visualization}}
{} % Location
{} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    %\item {Not understanding a thing during my brother's phd defense about support vector machines inspired me to take this course.}
    \item {This course is covered the statistical data visualization python library seaborn.}
    \item {Certificate of accomplishment: https://tinyurl.com/bdee5xwk}
  \end{cvitems}
}
\newline

%---------------------------------------------------------
\cventry
{Kaggle.com, Online Machine-Learning Community} % Affiliation/role
{\textit{Feature Engineering}}
{} % Location
{} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    %\item {Not understanding a thing during my brother's phd defense about support vector machines inspired me to take this course.}
    \item {This course on feature engineering covers techniques necessary to create more effective features for ML tasks and delves into topics like mutual information for feature selection, feature creation, clustering, PCA as well as target encoding for categorical data.}
    \item {Certificate of accomplishment: https://tinyurl.com/2u7kbxyh}
  \end{cvitems}
}
\newline

%---------------------------------------------------------
\cventry
  {John Hopkins University, Online} % Affiliation/role
  {\textit{Computing for Data Analysis}} % Organization/group
  {Grade: 97\%} % Date(s)
  {} % Location
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {This course covered the basics of data analysis and visualization in R in a medical context.}
      \item {Certificate of accomplishment: http://tinyurl.com/2ez3unkj}
    \end{cvitems}
  }
  \newline

  \cventry
  {Seqera.io, Online} % Affiliation/role
  {\textit{Nextflow and nf-core community training}} % Organization/group
  {2023} % Date(s)
  {} % Location
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {The training gave an introduction to scientific workflow system Nextflow and nf-core and covered basic deployment as well as development of nextflow nf-core pipelines.}
    \end{cvitems}
  }
  \newline


%---------------------------------------------------------
\cventry
  {Udemy, Online} % Affiliation/role
  {\textit{The Complete JavaScript Course 2023: From Zero to Expert!}} % Organization/group
  {} % Date(s)
  {} % Location
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {This course is a 69 hours complete and in-depth course covering fundamentals and advanced topics of JavaScript development.}
      \item {Curriculum: https://www.udemy.com/course/the-complete-javascript-course/}
      \item {Certificate of accomplishment: https://tinyurl.com/mrxc5h3x}
    \end{cvitems}
  }
  \newline

%---------------------------------------------------------
\cventry
  {Udemy, Online} % Affiliation/role
  {\textit{Node.js, Express, MongoDB \& More}} % Organization/group
  {Ongoing} % Date(s)
  {} % Location
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {This course covers backend engineering in JavaScript and focuses on building a secure and versatile RESTful API using Node.js, Express.js, MongoDB, and more.}
      \item {Curriculum: https://www.udemy.com/course/nodejs-express-mongodb-bootcamp/}
    \end{cvitems}
  }
  \newline

%---------------------------------------------------------
\cventry
  {Self-taught} % Affiliation/role
  {\textit{Full stack web development}} % Organization/group
  {} % Date(s)
  {} % Location
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Setup and administration of headless Linux systems.}
      \item {Applied SQL-like databases and the NoSQL database elasticsearch in a website environment.}
      \item {Used python model-view-controller frameworks django and flask + SQLAlchemy.}
      \item {Applied caching technology like memcached and redis to speed up website performance.}
      \item {Learned html, css, templating and javascript for front-end use.}
    \end{cvitems}
  }
%---------------------------------------------------------
\end{cventries}
