%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}
\begin{cventries}
\cventry
    {}
    {Peer Reviewed Journal Articles}
    {}
    {}
    {
\begin{cvitems}
    \vspace{-1\baselineskip}
    \setlength\itemsep{.5em}
    \item Brandon M. Butler, Avishek Kumar, S. Banu Ozkan. Dynamic allosteric residue coupling reveal disease mechanism for Gaucher disease and nSNVs across the proteome. (Submitted, Equal Contributor)
    \item Butler BM, Kazan IC, Kumar A, Ozkan SB (2018) Coevolving residues inform protein dynamics profiles and disease susceptibility of nSNVs. PLoS Comput Biol 14(11): e1006626. https://doi.org/10.1371/journal.pcbi.1006626
    \item Avishek Kumar, Syed Ali Asad Rizvi, Benjamin Brooks, R. Ali Vanderveld, Kevin H. Wilson, Chad
Kenney, Sam Edelstein, Adria Finch, Andrew Maxwell, Joe Zuckerbraun, and Rayid Ghani. 2018.
Using Machine Learning to Assess the Risk of and Prevent Water Main Breaks. In Proceedings of the
24th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining (KDD '18).
ACM, New York, NY, USA, 472-480. DOI: https://doi.org/10.1145/3219819.3219835
\end{cvitems}
}

\cventry
    {}
    {Peer Reviewed Journal Articles (Continued)}
    {}
    {}
    {
\begin{cvitems}
    \vspace{-1\baselineskip}
    \setlength\itemsep{.5em}
    \item Avishek Kumar, Brandon M. Butler, Sudhir Kumar, Sefika B. Ozkan. Integration of structural
dynamics and molecular evolution via protein interaction networks: a new era in genomic medicine.
Current Opinion In Structural Biology 35, 135 (2015)
    \item Sean L. Seyler, Avishek Kumar, M.F. Thorpe, and Oliver Beckstein. Path Similarity Analysis: A
method for Quantifying Macromolecular Pathways. PLoS Comput Biol (10): e1004568 (2015).
    \item Avishek Kumar, Paul Campitelli, M.F. Thorpe, S. Banu Ozkan, Partial Unfolding and refolding for
structure refinement: A unified approach of geometric simulations and molecular dynamics. Proteins:
Structure, Function, and Bioinformatics 83(12), 2279 (2015)
    \item Avishek Kumar, T.J. Glembo, S. Banu Ozkan, The Role of Conformational Dynamics and Allostery in
Disease Development. Biophysical Journal 109(6),1273 (2015)
    \item W.G. Ellenbroek, Varda F Hagh, Avishek Kumar, M.F. Thorpe, Martin van Hecke, Rigidity Loss in
Disordered Systems: Three Scenarios. Phys. Rev. Lett. 114, 135501 (2015)
    \item Avishek Kumar, Mark Wilson, David Sherrington, M.F Thorpe, Ring statistics of silica bilayers.
Journal of Physics: Condensed Matter 26, 395401 (2014)
    \item Mark Wilson, Avishek Kumar, David Sherrington, M.F. Thorpe, Modeling vitreous silica bilayers.
Phys. Rev. B 87, 214108 (2013)
    \item D Van Tuan, Avishek Kumar, Stephan Roche, F. Ortmann, MF Thorpe, P Ordejon, Insulating behavior
of an amorphous graphene membrane. Phys. Rev. B 86 (12), 121408 (2012)
    \item Avishek Kumar, Mark Wilson, M.F. Thorpe, Amorphous graphene: a realization of Zachariasen’s
glass. Journal of Physics: Condensed Matter 24(48), 485003 (2012)
    \item Y Li, F. Inam, Avishek Kumar, M.F. Thorpe, D.A. Drabold, Pentagonal puckering in a sheet of
amorphous graphene. physica status solidi (b). doi: 10.1002/pssb.201147195 (2011)
\end{cvitems}
}



\cventry{}
    {Book Chapters}
    {}
    {}
    {\begin{cvitems}
    \vspace{-1\baselineskip}
    \setlength\itemsep{.5em}
    \item Using GPUs to Study Protein Evolution in Order to Understand Antibiotic Resistance, \textit{Strategies in Biomedical Data Science: driving force for innovation} by Jay A. Etchings
\end{cvitems}}




\end{cventries}
