%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventryextended
  {Senior DevOps Engineer} % Job title
  {Everest Engineering - Contract} % Organization
  {} % Location
  {October 2021- Current} % Date(s)
  {Engaged to help upgrade and move a large Australian retail conglomerate to
    the cloud, by braking down a large on premise monolith into cloud-native
    microservices leveraging mostly serverless platforms such as Lambda,ECS and
    RDS}
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Provisioned resources onto Amazon AWS utilizing CDK IaC (Python
                  and Typescript), and built reusable components to ensure
                  compliance standards,
                  high-availability, fault tolerance, and auto-scaling.}
      \item {Built and optimised new/existing automation pipelines in Jenkins
                  and implemented automated dependency updates}
      \item {Deployed a centralized monitoring system that includes "Chatops"
                  to alert on AWS metrics, custom application metrics, and
                  security metrics }
      \item {Implemented several API microservices leveraging AWS API Gateway
                  and Lambda functions.}
      \item {Right sized resources for performance and/or cost.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventryextended
  {Senior Cloud Engineer} % Job title
  {Australian Energy Market Operator (AEMO) - Contract}
  % Organization
  {} % Location
  {Nov 2020 - Oct 2021} % Date(s)
  {Working in the Cloud Operations team to uplift and standardize AEMOs move
    into
    Azure from on premises and/or other cloud providers.}
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designing and building standardised environments in Azure ARM IaC,
                  and building deployment pipelines in Azure Devops so
                  deployment is fully
                  automatic.}
      \item {Moved existing workloads to Azure in a automated, cost-effective,
                  scalable, and low maintenance manner.}
      \item {Uplift existing services to move to the use of SaaS products such
                  as
                  Azure AKS.}
      \item {Working with developer teams to optimise environments for cost
                  and/or speed.}
      \item {Worked with a core data team move ETL processes from legacy
                  systems
                  to a cloud first Azure based data platform.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventryextended
  {Senior DevOps Engineer} % Job title
  {AGL Energy - Full-time} % Organization
  {} % Location
  {Nov 2019 - Nov 2020} % Date(s)
  {This role is part of a combined Devops/SRE practice within the wholesale
    side
    of AGL. I
    worked with many different internal teams such as networks, development,
    operations, security
    and architecture}
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Uplifted general development practices such as:
                  \\
                  \begin{cvitems}
                    \item {Assisted development teams to adopt a sole git
                                repository
                                workflow and Azure devops for automation
                                pipelines}
                    \item {Implemented an automated testing framework to use
                                within
                                deployment pipelines}
                    \item {Implemented performance testing and tuning for
                                databases and
                                applications}
                    \item {Supported a cloud first architecture and design for
                                new systems
                                / major updates \\}
                  \end{cvitems}
            }
      \item {Built environments utilizing Terraform and ARM, and created
                  modules
                  to standardize deployments.}
      \item {Assisting of containerization onto AKS of legacy applications to
                  reduce the number of VMs, and increasing up time and compute
                  scaling
                  possibilities.}
      \item {Implemented Backup and DR strategies, and a dashboard to monitor
                  systems for the SRE team. }
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventryextended
  {Lead Data Consultant} % Job title
  {Mantel group / CMD - Contract} % Organization
  {} % Location
  {Apr 2019 – Dec 2019} % Date(s)
  {Engagements include :} % Description(s) of tasks/responsibilities
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Lead a small team that designed, deployed, and integrated into
                  current
                  systems(AD, network, file storage) and supported a company
                  wide Data
                  Platform for a tier 1
                  energy provider}
      \item {Built and deployed a serverless ETL system to process customer
                  data and allow it to be accessed seamlessly via snowflake,
                  and also
                  helped uplift capabilities within the clients data team with
                  training
                  sessions.}
      \item {This included technologies such as Matillion, Tableau, Domino Data
                  Lab,
                  Gitlab,Snowflake and AWS products such as S3,Lambda,
                  Cloudformation, SNS,
                  SSM.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventryextended
  {Senior DevOps Engineer} % Job title
  {Contino} % Organization
  {} % Location
  {Apr 2019 – Dec 2019} % Date(s)
  {Engagements include :} % Description(s) of tasks/responsibilities
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Part of a small team that designed, developed, deployed and
                  supported in both a company wide Data Platform / ETL
                  Framework for a large
                  private health insurance company. This included technologies
                  such as Apachie
                  Airflow, Jenkins, Spark,  Terraform and Packer , and AWS
                  products such as S3,
                  EMR, Glue, Kinesis, and Redshift. This allowed the company
                  significant
                  flexibility, and allowing for future growth.}
      \item {Part of a small team that did development, deployment,
                  enhancements and support of a datalake and ETL framework for a large Australian
                  airline. This included AWS offerings like S3, EMR, Redshift, Lambda, Code
                  pipeline and Batch, as well as technologies such as Apache Airflow and Spark to
                  produce a resilient data processing platform. }
      \item {Built and deployed Amazon WorkSpaces for external developers, integrated into Azure AD.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventryextended
  {Senior Software developer / Devops engineer} % Job title
  {Stratton finance / Carsales.com.au} % Organization
  {} % Location
  {July 2016 – June 2018} % Date(s)
  {This role is a mixed technologies role,  split between Software development ( Windows services / web systems /
    databases) and a DevOps role (BASH/Powershell scripting,. AWS, Jenkins, Ansible) }
  % Description(s) of tasks/responsibilities
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Development:
                  \\
                  \begin{cvitems}
                    \item {Successfully designed and implemented an internet platform to allow customer’s to
                                electronically sign legal documents for
                                multiple tier 1 lending companies. This increased loan conversions by 35\% and
                                increased the
                                clients satisfaction results by allowing clients to fill in contracts anywhere at any
                                time.}
                    \item {Implemented legal compliance systems and procedures, as well as reports system outlining
                                breaches. This resulted in a 15\% increase on overall compliance across the company.}
                    \item {Worked with a team of BI and data scientists to create a system that uses machine learning
                                to optimize sales procedures, as well as Tableau reports and a data warehouse. }
                    \item {Worked with multiple teams to increase general systems and day to day procedure security
                                \\\\}
                  \end{cvitems}
            }
      \item{DevOps:
                  \\
                  \begin{cvitems}
                    \item {Automated the CI/CD pipelines using Jenkins, Vagrant/Ansible, MSbuild, ANT, and Powershell/Bash.
                                This increased the entire development teams output and allowed movement to a more Agile process.}
                    \item {Moved many critical systems (MSSQL databases / IIS servers / app and file servers)  to AWS
                                infrastructure across multiple availability zones, or re-implemented them using server less technologies (logging
                                systems, system testing systems).}
                    \item {Automating the help desk and infrastructure systems to help them improve general throughput and
                                increase the ease of on boarding new employees and general business tasks.}
                    \item {Wrote custom monitoring and integrated monitoring methods into deployment processes.}
                    \item {Was a major contributor to moving the software team from SVN to GIT.}
                    \item {Performed DevOps tasks, such as automating deployment on to EC2, for Linux and Windows platforms.\\
                          }
                  \end{cvitems}
            }
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Senior Software developer / Technical Team Lead } % Job title
  {SEMA Group} % Organization
  {} % Location
  {July 2015 – July 2016} % Date(s)
  {}  % Description(s) of tasks/responsibilities

  %---------------------------------------------------------
  \cventry
  {Lead Software developer} % Job title
  {Medical Indemnity Protection Society (MIPS.com.au)} % Organization
  {} % Location
  {Sep 2013 – July 2015} % Date(s)
  {}  % Description(s) of tasks/responsibilities

  %---------------------------------------------------------
  \cventry
  {Lead Software developer / DevOps Engineer - Contract} % Job title
  {SOY Group (Stuckonyou.com.au / PennyScallan.com.au)} % Organization
  {} % Location
  {Jul 2013 – Sep 2013} % Date(s)
  {}  % Description(s) of tasks/responsibilities

  %---------------------------------------------------------
  \cventry
  {Senior Software Developer} % Job title
  {Eftel Group / M2 Telecommunications} % Organization
  {} % Location
  {Feb 2013 – Jul 2013} % Date(s)
  {}  % Description(s) of tasks/responsibilities

  %---------------------------------------------------------
  \cventry
  {Senior Software Developer} % Job title
  {Lonsec Fiscal / SuperRatings} % Organization
  {} % Location
  {2011 - 2013} % Date(s)
  {}  % Description(s) of tasks/responsibilities

  %---------------------------------------------------------
  \cventry
  {Lead Software Engineer } % Job title
  {BCAV Holdings /  StoreSpecials.com.au /  LastChanceAds.com} % Organization
  {} % Location
  {20019 - 201} % Date(s)
  {}  % Description(s) of tasks/responsibilities

  %---------------------------------------------------------
  \cventry
  {Software Engineer - Contract} % Job title
  {C.R. Kennedy \& Company} % Organization
  {} % Location
  {Feb 2008 - Jul 2008} % Date(s)
  {}  % Description(s) of tasks/responsibilities

  %---------------------------------------------------------
  \cventry
  {Embedded Windows Software Engineer} % Job title
  {Datalink Technologies Pty.Ltd} % Organization
  {} % Location
  {2007 - 2009} % Date(s)
  {}  % Description(s) of tasks/responsibilities

  %---------------------------------------------------------
  \cventry
  {SQL DBA / .NET Developer} % Job title
  {Commission Monster Pty. Ltd / Viva 9 Pty. Ltd} % Organization
  {} % Location
  {2005 - 2007} % Date(s)
  {}  % Description(s) of tasks/responsibilities

  %---------------------------------------------------------
  \cventry
  {Graduate .Net Developer} % Job title
  {C – Learning  Pty. Ltd / Monash University Learning fast} % Organization
  {} % Location
  {2004 - 2005} % Date(s)
  {}  % Description(s) of tasks/responsibilities

  %---------------------------------------------------------
\end{cventries}