%\section{Experience}

\section{Product Development / R\&D}

%\emph{Experience separated into categories. Overlaps denote multiple concurrent roles.}

%\subsection{R\&D / Product Development / Managerial}
\cventry{2015 -- 2021}{Researcher Associate}{University of Bamberg (Third-Party Projects)}{}{Germany}{Designed and delivered data management solutions for a computer-aided manufacturing project which included companies such as Airbus (explorative/R\&D project).}


\cventry{2011 -- 2013}{Team Leader / Software Architect / R\&D Engineer}{TayaIT}{Cairo}{Egypt}{Led the development of several iOS apps and games as product owner (reported to the CEO), built architectures, computer (AI) players; responsible for aligning the technical, marketing, and strategy teams.}



\section{Academic / Managerial}


\cventry{2013 -- 2015}{Lecturer / Managerial Roles}{University of Technology Twintech}{}{Yemen}{Carried out managerial duties (reporting to the university president) and taught several courses (ex., Object Oriented Programming, Art \& Design History, Human-Computer Interaction).}


\cventry{2008 -- 2012}{Teaching Assistant}{The German University in Cairo (GUC)}{Cairo}{Egypt}{Taught 10 hours per week of tutorials, in addition to grading and exam correction (courses: Introduction to Artificial Intelligence, Introduction to Computer Science, Introduction to Computer Programming).}

\section{Education}
\cventry{2019 -- 2023}{Ph.D.}{The University of Bamberg}{Germany (\emph{Prospective})}{}{}%{Thesis: The Basin Network: A Model for Sharing and Exchanging Data}  % arguments 3 to 6 can be left empty
\cventry{2009 -- 2010}{MSc.}{Faculty of Engineering, The German University in Cairo (GUC)}{Egypt}{}{}%{Thesis: Multi-modal Perception as Grounded Focussed Belief Revision}
\cventry{2003 -- 2008}{BSc.}{Faculty of Engineering, The German University in Cairo (GUC)}{Egypt}{}{}








\newpage








\section{Technical}
\begin{cvcolumns}
  \cvcolumn{Good Familiarity}{Python, Neo4j, Prolog, git, \LaTeX, Linux CLI, Lisp, Java (v5)}
  \cvcolumn{Past Experience}{SQL, MongoDB, UML, Redis, Pearl, C++, Lucene, Micro-C programming}
\end{cvcolumns}

\vspace{-3.5ex}

%\cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

\section{Projects}
%Projects I was involved in one or more capacities: product owner, architect, organizer, and developer.  
%\cvitemwithcomment{2016 -- 2022}{\textbf{Basin Net}: A model for data exchange across organizations.}{PhD project}
\cvitemwithcomment{2017 -- 2020}{\textbf{kgservice}: A semantic graph database interface.}{\textcolor{blue}{\href{https://github.com/simutool/kgservice}{\faGithub/simutool/kgservice}}}{}
\cvitemwithcomment{2019}{\textbf{aku-client}: Meta-data client of the kgservice.}{\textcolor{blue}{\href{https://github.com/simutool/aku-client}{\faGithub/simutool/aku-client}}}{}
\cvitemwithcomment{2018}{\textbf{om-tool}: A tool to visualize and enrich sensor data.}{\textcolor{blue}{\href{https://github.com/simutool/om-tool}{\faGithub/simutool/om-tool}}}{}
%\cvitemwithcomment{2017}{\textbf{dm-reader}: Maps an ontology from excel to python dicts.}{\textcolor{blue}{\href{https://github.com/simutool/dm-reader}{\faGithub/simutool/dm-reader}}}{}
\cvitemwithcomment{2017}{\textbf{model-builder}: Loads an ontology to a Neo4j graph.}{\textcolor{blue}{\href{https://github.com/simutool/model-builder}{\faGithub/simutool/model-builder}}}{}
\cvitemwithcomment{2005 -- 2015}{A detailed portfolio for this period can be retrieved from:}{\textcolor{blue}{\href{https://bit.ly/3HTuluG}{bit.ly/3HTuluG}}}

\section{Languages}
\begin{cvcolumns}
  \cvcolumn{English}{Fluent}
  \cvcolumn{Arabic}{Fluent}
  \cvcolumn{German}{B1 (Telc Certificate)}  
\end{cvcolumns}

\vspace{-3.5ex}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): 
\renewcommand{\refname}{Publications}
\nocite{*}
\bibliographystyle{unsrt}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file


\section{References}
\cvitemwithcomment{}{\textbf{Daniela Nicklas}, \textit{Professor}, University of Bamberg}{}
\cvitemwithcomment{}{\textbf{Haythem Ismail}, \textit{Dean}, MET Faculty, The German University in Cairo}{}
\cvitemwithcomment{}{\textbf{Ashraf Tawwakol}, \textit{Co-founder}, Intersection; formerly, \emph{CEO}, TayaIT}{}
\cvitemwithcomment{}{\textbf{Wael Alaghbari}, \textit{President}, International University of Technology Twintech}{}

