\cvsection{Technologies}
\begin{cvskills}
  \cvskill {Languages} {Java, Python, Javascript, R}
  \cvskill {Databases} {MySQL, Cassandra, Redis, Elasticsearch, Redshift}
  \cvskill {DevOps} {Docker, Logstash, Chef, Graphite, StatsD, AWS CLI}
\end{cvskills}


%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Technical Lead} % Job title
    {Clir Renewables} % Organization
    {Richmond, BC, Canada} % Location
    {April 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team lead for 3 software developers creating a wind farm analysis tool with a Python backend and React frontend.}
        \item {Responsible for architecting the system, mentoring junior developers, and writing code.}
        \item {Setup infrastructure including a build server, user tracking, and secret management.}
        \item {Restructured the AWS deployment, defining security groups, IAM roles, and VPC subnets.}
        \item {Migrated time-series data from Elasticsearch into Redshift for reliability and speed.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Principal Software Engineer} % Job title
    {Pulse Energy (Acquired by EnerNOC then Yardi)} % Organization
    {Vancouver, BC, Canada} % Location
    {September 2008 - April 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a time-series database in Java using Cassandra to store terabytes of smart meter data.}
        \item {Designed a tariff engine in node.js for modeling energy costs.}
        \item {Handled technical recruiting for new developers, including managing the coding challenge.}
        \item {Wrote Chef recipes to provision our cloud infrastructure in EC2.}
        \item {Setup a monitoring stack using Logstash, Kibana, Graphite, Statsd, and a custom Graphiti-fork.}
        \item {Patented an algorithm for forecasting energy use based on historical conditions and current weather.}
        \item {Mentored junior developers on our team, teaching them fundamentals in code design and software life-cycles.}
        \item {Optimized code for other teams (in Java, Python, Ruby, and R) to reduce memory footprints and speed up execution.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Business Objects (Acquired by SAP)} % Organization
    {Vancouver, BC, Canada} % Location
    {July 2006 - September 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed server-side components in C++ and Java.}
        \item {Feature owner of licensing technology and Java container server.}
        \item {Quickly learned new codebases and helped with features that were behind schedule.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Programmer Analyst (Co-op)} % Job title
    {Morgan Stanley} % Organization
    {London, England} % Location
    {August - December 2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked for the Credit Derivative Swap (CDS) team.}
        \item {Created C\# GUI component to view historical data.}
        \item {Integrated a third-party distributed cache to store real-time market data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Design Engineer in Test (Co-op)} % Job title
    {Microsoft} % Organization
    {Redmond, WA, USA} % Location
    {January - April 2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created quality measurement tool for MSN Newsbot that revealed several weaknesses.}
        \item {Improved Newsbot’s algorithm to return more relevant content for Canadian users.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
