%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Research Fellow} % Job title
    {Indian Institute of Technology Delhi} % Organization
    {New Delhi, India} % Location
    {May 2014 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on the force control of a KUKA robot to perform the task of inserting a peg in a hole.}
        \item {Development of RoboAnalyzer software which helps in teaching and learning of robot kinematics and dynamics in an easier and funnier way.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Staff} % Job title
    {Indian Institute of Technology Delhi} % Organization
    {New Delhi, India} % Location
    {Feb. 2014 - May 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Involved in a collaborative project ``SAKSHAR: An Image-projective Desktop Varnamala Trainer (IDVT) for interactive learning of alphabets''.}
        \item {The project aims to make primary education more attractive and fun towards the kids.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software QA Engineer} % Job title
    {Altair Engineering} % Organization
    {Bangalore, India} % Location
    {Jun. 2012 - Jan. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Successfully performed software testing such as performance, load, and functional testing of Altair Web Portal Framework and Compute Manager, a web-based interface for PBS workload manager.}
        \item {Developed a framework for automated testing of REST Services.}
        \item {Key person for guaranteeing essential functionality such as licensing of Altair Web Portal Framework.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
